---
title: "<b>Data cleaning and analysis for:</b><br>Climate change belief system</br>"
author: "Sanguk Lee, Matthew H. Goldberg, Seth A. Rosenthal, and Anthony Leiserowitz"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
---

<style type="text/css">

h1.title {
  font-size: 38px;
  color: Black;
  text-align: center;
}
h4.author {
    font-size: 28px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
h4.date {
  font-size: 20px;
  font-family: "Times New Roman", Times, serif;
  color: Black;
  text-align: center;
}
</style>

```{r data_load, include=F}
#Loading packages
library(tidyverse)
library(foreign)
library(dplyr) 
library(bootnet) 
library(ggplot2)
library(readxl) 
library(patchwork) 
library(emmeans) 
library(ggpubr)
library(qgraph)
```

```{r setup, include=F}
# load the data
df1 <- read.csv("GW_belief_system_data.csv")
```

## Network

```{r All_network_estimation, echo=FALSE, message=FALSE, warning=FALSE}
######## Network Overall #########
# drop wave variable
df2 <- df1[,3:17]
# let's build network 
labels <- c("GW \nhappening","GW \nhuman cause","GW \nconsensus","Collective \nefficacy",
          "GW \nworry","Community \nrisk","US \nrisk","Risk \ntime",
          "General \nattitude",
          "Policy \nsupport \nCO2","Policy \nsupport \nfund","Policy \nsupport \nrebate",
          "Political \nbehavior","Consumer \nbehavior \nreward","Consumer \nbehavior \npunish")
net_all <- estimateNetwork(df2, default = "EBICglasso", labels = labels)
```

```{r All_network_plot, echo=FALSE, message=FALSE}
fig1<-plot(net_all, layout = "spring", labels = labels, label.cex =.8,label.scale = F,title ="")
```

## RQ1 Centrality

## Centrality
*Betweenness Centrality: The degree to which a node lies on the shortest path between other nodes.
*Closeness Centrality: The degree to which a node is close to all other nodes.
*Strength Centrality: The degree to which a node is strongly connected to other adjacent nodes in the network.

```{r RQ1_centrality, echo=F, message= F, cache = T}
# estimate parameters of network including centrality and edge weights

#set.seed(555) 
# net_boot <- bootnet(net_all, nBoots = 1000,
#                     default = "EBICglasso",
#                     statistics = c("betweenness","closeness","strength","edge"),
#                     type = "nonparametric", nCores = 1)

#save(net_boot, file= paste0(getwd(),"/data/network_data_for_replication.RData"))

load(paste0(getwd(),"/data/network_data_for_replication.RData"))

net_boot_whole <- net_boot$bootTable
net_boot_strength <- net_boot_whole %>%
  filter(type=="strength") %>%
  filter(id == c("US \nrisk","GW \nworry"))

net_boot_stat<-summary(net_boot)
net_boot_stat_cent <- net_boot_stat %>%
  filter(type!="edge")
```


```{r customized_centrality_Plot, echo=FALSE, message=FALSE}
# What is in the center? worry is positioned in the center
cent_stat <- net_boot_stat_cent %>%
  dplyr::select(type, id, mean, CIlower, CIupper)

labels2 <- c("Collective efficacy", "Community risk", "Consumer behavior punish", 
             "Consumer behavior reward", "GW consensus", "GW happening", "GW human cause", "GW worry", 
             "General attitude", "Policy support CO2", "Policy support fund", "Policy support rebate", 
             "Political behavior", "Risk time", "US risk")

cent_stat$labels <- rep(labels2, 3)

beet_cent<- cent_stat %>%
  filter(type == "betweenness")
beet_cent <- beet_cent[order(beet_cent$mean,decreasing = T),]
rev(unique(beet_cent$labels))
cent_stat$labels <- factor(cent_stat$labels, levels= rev(unique(beet_cent$labels)))

cent_stat$type <- factor(cent_stat$type, labels= c("Betweenness", "Closeness", "Strength"))

fig_cent<- ggplot(data = cent_stat, aes(x=mean, y=labels)) +
  geom_point(size=1) + 
  geom_errorbar(aes(xmin=(CIlower), xmax=(CIupper)), stat = "identity", position=position_dodge(0.1), width=.1) +
  xlab("") +
  ylab("") + 
  geom_vline(xintercept = 0, linetype = "dotted", alpha = .3)+
  theme_bw() +
  facet_wrap(~type, scales = "free_x") +
  theme(axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 7),
        strip.text.x = element_text(size = 7))
fig_cent
ggsave(paste0(output, "Centrality_revise.tiff"), 
       plot = last_plot(), 
       width = 14, 
       height = 10, 
       units = "cm", 
       dpi = 300)
```


```{r party_count, include = F}
count <- df1 %>% count(PartyWLeaners)
rep <- count[1,2]
dem <- count[2,2]
ind <- count[3,2]
no <- count[4,2]
```

# Network by Party
(Republican _n_ = `r rep`, Democratic _n_ = `r dem`, Independent _n_ = `r ind`, No Party _n_ = `r no`)

## Network
```{r Party_network_plot, echo=TRUE, message = FALSE, warning=F}
# network by party
netp <- function(dataframe,p_group){
  dfs <- dataframe[which(dataframe$PartyWLeaners==p_group),]
  dfs <- dfs[,3:17]
  net <- estimateNetwork(dfs, default = "EBICglasso", labels = labels)
}
missing_p<-function(dataframe,p_group){
  dfs <- dataframe[which(dataframe$PartyWLeaners==p_group),]
  dfs <- dfs[,3:17]
  missing_perc <- sum(is.na(dfs))/(nrow(dfs)*ncol(dfs))*100
  print(missing_perc)
}
# remove disengaged group since they have many missing values in risk questions
p_list<- c("Republicans","Democrats","Independent/Other","No party/Not interested")
net_list_p <- list()
for (p in p_list){
  net<-netp(df1,p)
  net_list_p <- append(net_list_p, list(net))
  #missing_p(df1,p) # no party group has more than 10% missing values
}

plot(net_all, layout = "spring", labels = labels, label.cex =.8,label.scale = F,title ="")
plot(net_list_p[[1]], layout = "spring", labels = labels, label.cex =0.8,label.scale = F,title="")
plot(net_list_p[[2]], layout = "spring", labels = labels, label.cex =0.8,label.scale = F,title="")
plot(net_list_p[[3]], layout = "spring", labels = labels, label.cex =0.8,label.scale = F,title="")
plot(net_list_p[[4]], layout = "spring", labels = labels, label.cex =0.8,label.scale = F,title="")

```


```{r functions, include = FALSE, message = FALSE, warning=F}
# density of a weighted network (Ref: Liu, G., Wong, L., & Chua, H. N. (2009). Complex discovery from weighted PPI networks. Bioinformatics, 25(15), 1891-1897.)
density <- function(netdata){
  sum_v <- sum(abs(netdata$graph)) # use absolute values. 
  num_nodes<- netdata$nNode
  possible_edges<- netdata$nNode*(netdata$nNode-1)  # compute the number of possible edges
  result <- sum_v/possible_edges
  return(result)
}

# Get lower triangle of the correlation matrix
get_lower_tri<-function(cormat){
  cormat[upper.tri(cormat)] <- NA
  return(cormat)
}
```

## Density

* Density: The degree of network tightness 

# Network by Wave

## Density Change

```{r network_by_pol_wave, include = F}
# define a function that generates graph
# data = dataframe
net_p_wave<- function(dataframe, wave2, pol2){
  dfwp <- dataframe %>%
    filter(wave == wave2 & PartyWLeaners == pol2)
  dfwp <- dfwp[,3:17]
  net <- estimateNetwork(dfwp, default = "EBICglasso", labels = labels)
  return(net)
}
```

```{r density_plot_by_pol_wave, echo=FALSE, message = FALSE, warning=F}
# looping to generate 60 networks based on wave and party, and keep them in a list
net_list_wp<- list()
for (w in wave_list){
  net_list_w1 <- list()
  for (p in p_list){
    net <- net_p_wave(df1, w, p)
    net_list_w1 <- append(net_list_w1, list(net))
    }
  net_list_wp <- append(net_list_wp, list(net_list_w1))
}

# does network density has increased over time across parties?
library(lubridate)

dens_wp <- list()
for (w in 1:length(wave_list)){
  dens_p <- list()
  for (p in 1:length(p_list)){
    net <- net_list_wp[[w]][[p]] # w = (1,2,3,4,5...15) p = (rep,demo,ind,no)
    dens <- density(net)
    dens_p <- append(dens_p, list(dens))
  }
  dens_wp <-append(dens_wp, list(dens_p))
}

# density df
dens_df<- as.data.frame(do.call(rbind, dens_wp))
names(dens_df) <- p_list
dens_df <- dens_df %>% 
  gather(pol, density, 1:4)
dens_df$wave <- rep(wave_list, 4)

df_net<-dens_df
df_net$wave <- mdy(df_net$wave)
df_net$wave <- as.Date(df_net$wave, "%m/%y")

df_net$density <- as.numeric(df_net$density)
df_net$pol <- factor(df_net$pol, levels = p_list)

mean(df_net$density)
sd(df_net$density)

dens_plot <- ggplot(data = df_net, aes(x = wave, y = density, color = pol)) +
  geom_point() + 
  scale_color_manual(values = c('#FF3300', '#3399FF', "#99FF33", "#FFCC00")) +
  geom_smooth(method = lm) +
  ylim(c(0, 0.10)) +
  labs(title = "", x = "Wave", y = "Density", color = "Political Affiliation") +
  theme(legend.key.size = unit(0.5, "cm"),
        legend.text = element_text(size = 6),
        axis.text = element_text(size = 6),
        axis.title = element_text(size = 8)) +
  theme_classic()
dens_plot 
```

## RQ2 Density Regressions & Simple slope

```{r RQ2_reg1, echo=FALSE, message = FALSE, warning=F}
# set up
df_net$wave_num <- rep(1:15, 4)
df_net$pol_factor<- as.factor(df_net$pol)

# regression
model1 <- lm(density~ wave_num*pol_factor, df_net)
#model1 <- lm(scale(density)~ scale(wave_num)*pol_factor, df_net)
coef(model1)
summary(model1)
confint(model1)

# simple slope
emtrends(model1, ~ pol_factor, var = "wave_num")
```


```{r melted_wp, echo=FALSE, message = FALSE, warning=F}
library(NetworkDistance)
library(reshape2)

graph_list_wp <- list()
for (w in 1:length(wave_list)){
  graph_p <- list()
  for (p in 1:length(p_list)){
    net_wp <- net_list_wp[[w]][[p]]$graph
    graph_p <- append(graph_p, list(net_wp))
  }
  graph_list_wp <- append(graph_list_wp, list(graph_p))
}

renquote <- function(l){
  if (is.list(l)) lapply(l, renquote) 
  else enquote(l)}
graph_list_wp_unflat<-lapply(unlist(renquote(graph_list_wp)), eval)
# reorder list 
# rep: first 15 waves 
# demo: second 15 waves 
# ind: third 15 waves 
# no: fourth 15 waves 
myorder <- list(1,5,9,13,17,21,25,29,33,37,41,45,49,53,57,
            2,6,10,14,18,22,26,30,34,38,42,46,50,54,58,
            3,7,11,15,19,23,27,31,35,39,43,47,51,55,59,
            4,8,12,16,20,24,28,32,36,40,44,48,52,56,60)
new_graph_list_wp <- list()
for (l in myorder){
  graph <- graph_list_wp_unflat[[l]]
  new_graph_list_wp <- append(new_graph_list_wp,list(graph))
}

GDD_wp <- nd.gdd(new_graph_list_wp, out.dist = FALSE)

# Get lower triangle of the correlation matrix
lower_tri_wp <- get_lower_tri(GDD_wp$D)
melted_wp <- melt(lower_tri_wp, na.rm = T)

# normalize the graph diffusion distance score using min-max method
normalize <- function(x) {
  return((x - min(x)) / (max(x) - min(x)))
}

# Apply the function to the "value" column
melted_wp$value <- normalize(melted_wp$value)
```

```{r setup_for_RQ3, include=FALSE, message = FALSE, warning=F}
# recode var1 and var2
melted_wp <- melted_wp %>%
  mutate(revar1 = case_when(Var1 %in% 1:15 ~ "rep",
                   Var1 %in% 16:30 ~ "demo",
                   Var1 %in% 31:45 ~ "ind",
                   Var1 %in% 46:60 ~ "no"))
melted_wp <- melted_wp %>%
  mutate(revar2 = case_when(Var2 %in% 1:15 ~ "rep",
                   Var2 %in% 16:30 ~ "demo",
                   Var2 %in% 31:45 ~ "ind",
                   Var2 %in% 46:60 ~ "no"))
melted_wp$dyadic_cond <- 0 
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="rep", "rep-rep", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="demo", "rep-demo", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="ind", "rep-ind", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="no", "rep-no", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="rep", "rep-demo", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="demo", "demo-demo", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="ind", "demo-ind", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="no", "demo-no", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="rep", "rep-ind", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="demo", "demo-ind", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="ind", "ind-ind", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="no", "ind-no", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="rep", "rep-no", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="demo", "demo-no", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="ind", "ind-no", melted_wp$dyadic_cond)
melted_wp$dyadic_cond <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="no", "no-no", melted_wp$dyadic_cond)
melted_wp <- melted_wp[which(melted_wp$value > 0 ), ]
melted_wp$dyadic_cond <- as.factor(melted_wp$dyadic_cond)
melted_wp2 <- melted_wp[which(melted_wp$dyadic_cond =="rep-rep"|melted_wp$dyadic_cond =="demo-demo"|
                                melted_wp$dyadic_cond =="ind-ind"|melted_wp$dyadic_cond =="no-no"), ]
melted_wp3 <- melted_wp[which(melted_wp$dyadic_cond =="rep-demo"|melted_wp$dyadic_cond =="rep-ind"|
                                melted_wp$dyadic_cond =="rep-no"|melted_wp$dyadic_cond =="demo-ind"|
                                melted_wp$dyadic_cond =="demo-no"|melted_wp$dyadic_cond =="ind-no"), ]

melted_wp$dyadic_category <- 0 
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="rep", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="demo", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="ind", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="no", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="rep", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="demo", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="ind", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="no", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="rep", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="demo", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="ind", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="no", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="rep", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="demo", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="ind", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="no", "no-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- as.factor(melted_wp$dyadic_category)

melted_wp$dyadic_category <- 0 
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="rep", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="demo", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="ind", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="rep" & melted_wp$revar2=="no", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="rep", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="demo", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="ind", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="demo" & melted_wp$revar2=="no", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="rep", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="demo", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="ind", "party-party", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="ind" & melted_wp$revar2=="no", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="rep", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="demo", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="ind", "party-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- ifelse(melted_wp$revar1=="no" & melted_wp$revar2=="no", "no-no", melted_wp$dyadic_category)
melted_wp$dyadic_category <- as.factor(melted_wp$dyadic_category)

```

## Graph Diffusion Distance Within and Between Partisanship
* IV: dyadic partisanship condition 
* DV: graph diffusion distance

### Within Partisanship
```{r RQ3a_intra_group_comparison, echo=FALSE, message = FALSE, warning=F}
library("ggpubr")

table(melted_wp2$dyadic_cond)
melted_wp2$dyadic_cond <- factor(melted_wp2$dyadic_cond, 
                                 levels = c("rep-rep","demo-demo","ind-ind","no-no"),
                                 labels = c("Republican","Democratic","Independent","No Party"))

summary_melted_wp2 <- aggregate(value ~ dyadic_cond, melted_wp2, function(x) c(mean = mean(x), sd = sd(x)/sqrt(length(x))))
mean(melted_wp2$value)
sd(melted_wp2$value)

anova1 <- aov(value ~ dyadic_cond, data= melted_wp2)
summary(anova1)
#confint(anova1)

tukey <- TukeyHSD(anova1)
tukey
plot(tukey, las = 1)

ggplot(melted_wp2, aes(x= dyadic_cond, y = value)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(width = 0.2,alpha = 0.6, color = "gray80") +
  labs(y = "Normalized Graph Diffusion Distance Score", x = "") +
  theme_classic()+
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))+
  coord_cartesian(ylim = c(0, 1))

```

```{r RQ3a_sensitivity_test, echo=FALSE, message = FALSE, warning=F}
names(melted_wp2)
outliers <- melted_wp2 %>% 
  filter(revar1=="no") %>%
  mutate(value_scaled = scale(value)) %>%
  arrange(desc(value_scaled))

# Belief system of no party at wave 3 seems structurally very different from others potentially due to the many missignness in the data. 
# This contributes on producing outliers of GDD. 
# We need to examine whether the results will be replicated even after we remove outliers. 
# Belief system of no party at wave 3 = 48. Let's remove belief system 48 from the data
sen_melted_wp2 <- melted_wp2 %>%
  filter(Var1!=48&Var2!=48)

summary_sen_melted_wp2 <- aggregate(value ~ dyadic_cond, sen_melted_wp2, function(x) c(mean = mean(x), sd = sd(x)/sqrt(length(x))))

anova1<- aov(value ~ dyadic_cond, data= sen_melted_wp2)
summary(anova1)
#confint(anova1)

tukey <- TukeyHSD(anova1)
tukey
plot(tukey, las = 1)

ggplot(sen_melted_wp2, aes(x= dyadic_cond, y = value)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(width = 0.2,alpha = 0.6, color = "gray80") +
  labs(y = "Normalized Graph Diffusion Distance Score", x = "") +
  theme_classic()+
  theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 10))+
  coord_cartesian(ylim = c(0, 1))
    
```


### Between Partisanship
```{r RQ3b_inter_group_comparison, echo=FALSE, message = FALSE, warning=F}
anova2 <- aov(value ~ dyadic_cond, data= melted_wp3)
summary(anova2)
tukey2 <- TukeyHSD(anova2)
tukey2

melted_wp3$dyadic_cond <- factor(melted_wp3$dyadic_cond, 
                                 levels= c("rep-demo","rep-ind","demo-ind",
                                           "rep-no","demo-no","ind-no"),
                                 labels=c("Republican-Democratic","Republican-Independent","Democratic-Independent",
                                          "Republican-No Party","Democratic-No Party","Independent-No Party"))

mean(melted_wp3$value)
sd(melted_wp3$value)

ggplot(melted_wp3, aes(x= dyadic_cond, y = value)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(width = 0.2,alpha = 0.6, color = "gray80") +
  labs(y = "Normalized Graph Diffusion Distance Score", x = "") +
  theme_classic()+
  theme(axis.text.x = element_text(size = 9),
        axis.text.y = element_text(size = 10)) +
  coord_cartesian(ylim = c(0, 1))

```


```{r RQ3b_sensitivity_test, echo=FALSE, message = FALSE, warning=F}
names(melted_wp3)
outliers <- melted_wp3 %>% 
  filter(revar1=="no") %>%
  mutate(value_scaled = scale(value)) %>%
  arrange(desc(value_scaled))

# Belief system of no party at wave 3 seems structurally very different from others potentially due to the many missignness in the data. 
# This contributes on producing outliers of GDD. 
# We need to examine whether the results will be replicated even after we remove outliers. 
# Belief system of no party at wave 3 = 48. Let's remove belief system 48 from the data
sen_melted_wp3 <- melted_wp3 %>%
  filter(Var1!=48&Var2!=48)

summary_sen_melted_wp3 <- aggregate(value ~ dyadic_cond, sen_melted_wp3, function(x) c(mean = mean(x), sd = sd(x)/sqrt(length(x))))

anova1<- aov(value ~ dyadic_cond, data= sen_melted_wp3)
summary(anova1)
#confint(anova1)

tukey <- TukeyHSD(anova1)
tukey
plot(tukey, las = 1)

ggplot(sen_melted_wp3, aes(x= dyadic_cond, y = value)) +
  geom_boxplot(outlier.colour = NA) +
  geom_jitter(width = 0.2,alpha = 0.6, color = "gray80") +
  labs(y = "Normalized Graph Diffusion Distance Score", x = "") +
  theme_classic()+
  theme(axis.text.x = element_text(size = 9),
        axis.text.y = element_text(size = 10))+
  coord_cartesian(ylim = c(0, 1))
```

# Supplemntal Material

```{r bootstrap_centrality_difference, echo = FALSE, message = FALSE, warning = FALSE}
labels3 <- c("GW \nhappening","GW \nhuman cause","GW \nconsensus","Collective \nefficacy",
          "Community \nrisk","US \nrisk","Risk \ntime",
          "General \nattitude",
          "Policy \nsupport \nCO2","Policy \nsupport \nfund","Policy \nsupport \ntax",
          "Political \nbehavior","Consumer \nbehavior \nreward","Consumer \nbehavior \npunish")

diff_df <- data.frame(id1 = character(), id2 = character(), measure = character(),
                      lower = numeric(), upper = numeric(), significant = logical(),
                      stringsAsFactors = FALSE)

for (label in labels3) {
  row <- differenceTest(net_boot, label, "GW \nworry", c("betweenness","closeness","strength"), alpha = .05)
  diff_df<-rbind(diff_df,row)
}
```

## sensitivity, specifity, stableness tests for centrality of the whole network
```{r sensitivity, spcifity, stableness tests, echo = FALSE, message = FALSE, warning = FALSE}
load(paste0(getwd(),"/data/network_data_for_replication_net_boot2.RData"))
a<-net_boot2$bootTable
plot(net_boot2, statistics = c("betweenness","closeness","strength"))
ggsave(paste0(output,"stability.png"), width = 15, height = 12, units = "cm", dpi = 600)
corStability(net_boot2, cor= 0.7, statistics = c("betweenness","closeness","strength","edge"))
```

```{r descriptive_df1, echo=FALSE, message=FALSE, warning=FALSE}
names(df1)
df_desc <- df1[,3:17]
sapply(df_desc, function(x) c(mean = round(mean(x, na.rm = T),2), sd = round(sd(x, na.rm = T),2)))
```
